\part{Directions and Tips}

Delete this entire page before submitting FINAL logbook check (not before)

\begin{itemize}
    \item Remember that this is a legal document.
    \item Anyone should be able to follow exactly what you did in your project
          by reading your logbook. That's the level of detail you need.
    \item You MAY NOT delete any entries/data from this notebook. If you need to
          delete anything, you should strike through it (\menu{format > text >
          strikethrough}). You can also make multiple versions of your entries,
          if appropriate.
    \item If you did work on other documents, you may cut and paste the items
          from those other locations. Just provide citations/reference those
          other locations. If you can't cut \& paste easily (like you are
          referencing a physical lab notebook), you should decide if it's
          important to scan in the document or to just reference your previous
          work.
\end{itemize}

EVERY SKETCH OR DESIGN OR CODE you create should be included in your journal.
Every design change must be documented. If you have any physical lab set ups or
things you are building, include photos in your reflection entries. You must
have AT LEAST SOME PICTURES that include you doing work on your project.

\begin{itemize}
    \item Every day you work on a project, you should include a reflection entry
          with a summary of what you accomplished that day, any ideas you
          discussed, and other important ideas (even if you're not sure and are
          just considering them).
    \item Use your reflection entries to plan out what your next day should
          accomplish.
    \item At some point, you will need to do project planning, and you should
          include images of your project planning document (like a kanban board
          in your journal).
    \item Research/bibliography pages should be set up correctly using proper.
    \item If appropriate, title your entries (not reflection entries but other
          items in your lab notebook). You can insert ADDITIONAL sections in
          your logbook, but you must have everything in the template.
    \item Date all entries and put your initials. If you modify the entry, put
          modified dates and re-initial. You can also make version 1, 2, etc.\@
          for entries. Include page numbers
\end{itemize}
