\part{Initial Research Plan form 1A}

% TODO: See if need to be removed
\textbf{All projects must have a Research Plan}
\begin{enumerate}[label=\Alph*.]
    \item The Research Plan is to be written prior to experimentation following the instructions below to detail the rationale, research question(s), methodology, and risk assessment of the proposed research.
    \item If changes are made during the research, such changes can be added to the original research plan as an addendum, recognizing that some changes may require returning to the IRB or SRC for appropriate review and approvals. If no additional approvals are required, this addendum serves as a project summary to explain research that was conducted.
    \item If no changes are made from the original research plan, no project summary is required.
\end{enumerate}

% TODO: To be removed
% \textbf{The Research Plan/Project Summary should include the following}

\section{Rationale}

Include a brief synopsis of the background that supports your research problem and explain why this research is important and if applicable, explain any societal impact of your research.

\begin{field}
  
\end{field}

\section{Research Question}

\begin{field}
\end{field}

\section{Overall Hypothesis}

Include your independent and dependent variables AND justification for your hypothesis. Include a separate null hypothesis.

\subsection*{Hypothesis}

\begin{field}
\end{field}

\subsection*{Null Hypothesis}

\begin{field}
\end{field}

\section{Procedure}

Detailed procedures for your experimentation, including methods for data
collection, and when applicable, the source of data used.

\subsection{Independent Variable}
Including units and treatment levels to be tested

\begin{field}

\end{field}

\subsection{Dependent variable}
Including method of measurement and units

\begin{field}
   
\end{field}


\subsection{Control Group/Baseline defined with units}

\begin{field}

\end{field}

\subsection{Experimental controls}
Complete list of all variables that will remain constant between treatment levels

\begin{field}

\end{field}

\subsection{Materials/Tools/Equipment needed for testing (include quantities)}

\begin{field}
   
\end{field}

\subsection{Experimental procedure} 

Detail all procedures and experimental design including methods for data collection, and when applicable, the source of data used. This should be a numbered list, like you would have for a lab, specific enough for someone unfamiliar with your experiment to follow. Be sure to include the number of trials.

\begin{field}
  
\end{field}


\subsection{Risk and Safety}

Identify any potential risks and safety precautions needed.

\begin{field}

\end{field}

\subsection{Data Analysis}

Describe the procedures you will use to analyze the data/results. 

\begin{field}
   
\end{field}

\subsection{Bibliography}

List major references (e.g. science journal articles, books, internet sites) from your literature review.

\begin{field}
    \printbibliography[heading=none]
\end{field}
